\chapter{Vision}

This chapter explains the vision for the project.

\section{Current Situation}

In the growing sector of board and card games, companies started in the last few
years to letting produce their products as apps for mobile devices and
computers. This allows users to play their favorite board and card games on the
go without needing table space or over the internet with friends at different
places---as long as they have access to a plattform on which the developer
created an app for.

In contrast to native apps which have to be created for each operating system,
there is the web plattform which essentially is usable on every operating
system. This has the big advantage that apps for the web have to be created once
and can be used on every internet device---there is no need to develop and
maintain multiple apps to be able to target each user. Also, web apps can be
used without installation---this allows the userbase to grow fast as every
person who knows about the web app is immediately able to use it.

Until a few years ago, the web plattform had downsides which kept developers
from using its advantages: It was missing key functionalities (e.g.
no offline capabilities, no 3D graphics support, no \gls{peer-to-peer}
connections, and so on). With the stabilisation of the \gls{HTML5} ecosystem
this issue changed: A lot of new standards emerged which began to close the
functionality gap between native and web apps. While browser vendors are quick
to implement new standards in their respective browser, there was another issue:
Users were slow in adapting new versions of their web browsers. It was not
practically possible to use the new \gls{HTML5} functionality without excluding
a big part of the users who still are using old browser versions. This has
changed in the last years: Web browsers now are automatically updating as soon
as new versions are released. This assures that most of the users are able to
use those new functionalities and newly added functionalities are soon usable
for most of the existing users.

With both of the mentioned problems solved, developers are now able to make use
of the advantages of the web plattform. But as of today, there is no programming
library known to the author that allows creating board and card game
implementations without needing browser plugins (like Flash Player or Unity
Player) which destroy the web plattform advantages, as again installations are
needed and the plugin needs to exist for the user's operating system. Also there
is no such programming library known to the author that is both open source and
generic (to support different types of board and card games). As such, there
exists a lot of unused potential for board and card games on the web plattform.

\section{Goals}

As a part of this project, a programming library for the web plattform should be
created, allowing developers to easily create board and card game
implementations and as such make use of the advantages of the web plattform for
their board and card games. This framework should make use of the new
\gls{HTML5} functionalities like \gls{peer-to-peer} connections (and thus not
requiring a server for communication), taking away the need for every developer
to reinvent the wheel and to develop an own solution to the same problems.
Through a well-defined \gls{API} these inner workings should be taken away from
the board and card games implementation, allowing the developers to only care
about their game implementations.

The user should be able to navigate to a board or card game website with their
web browser to start a new game session. He should then be able to invite
friends by simply giving them the unique game session URL. Visiting these links,
the users automatically connect \gls{peer-to-peer} to each other, being able to
start useing the chosen board or card game. By reducing the connection process
for the user to just sharing and using an URL, the biggest advantages of the web
plattform can be used---no registration, searching by usernames, or similar
actions are required, which allows the players to directly jump into the game
with a single click.

Together with the \gls{API}, two board or card game implementations are part of
the project. This allows testing and showcasing the \gls{API}, giving practical
examples how to use the \gls{API} and showing that the \gls{API} is generic and
applicable to real world board and card games.

There are a few challanges for this project:

\begin{description}
  \item[Generic \gls{API}:] Designing an \gls{API} which allows the realization
  of as much different games as feasible while still not be overloaded.
  \item[\gls{API} design guiding developers:] Creating the \gls{API} design in a
  way that leads the developer to correctly using it and make it hard to use it
  in a wrong way. By example, as the library communicates over the network,
  timeouts could occur. It must not be possible for the developer to forget
  handling timeout errors leading to silent failures.
  \item[Trust control:] Being \gls{peer-to-peer} based, there is no trusted
  server to control or store \gls{hidden information}. Other players could use
  manipulated clients, so cheating should be prevented on the library level.
  By example, if a user plays a \gls{face}-down card, the other users
  do not know what is on the front side of the card, but the user must not be
  able to lie about the card's \gls{face} when revealing.
  \item[Distributed generation of randomness:] \Glspl{die} are a common element
  in board games. There must be a way to conjointly create pseudo-random numbers
  without needing to trust the other clients.
  \item[``Mental Poker Problem'':] Users must be able to draw cards from a
  shared, shuffled card pile without the other clients knowing which cards they
  are and without it being possible for multiple clients to draw the same
  ``physical'' card.
  \item[Reference implementations:] Finding two very different board or card
  games for the reference implementations to use as an example, to showcase all
  realized features and to show the abilities of the library.
\end{description}

\section{Motivation}

As there is no similar project known to the author, there is a high relevancy to
practice of this project. There is a high chance the result of the master thesis
and this project are going to be used by users wanting a simple,
installation-less possibility to compete in online board and card games, as well
as by publishers wanting to offer their games for promotional purposes or even
as a paid solution.

As the author's specialisation during the master studies have been modern web
technologies, he is very interested in this project, as it allows using multiple
new web technologies that have not been around a few years ago. As a student
project research thesis during the bachelor studies he worked on a web
application with \gls{peer-to-peer} video telephony as the core feature
\cite{blaser2013practical}. It will be interesting to see how the feature and
the browser support developed since then (as the specification was back then and
still is in the Working Draft status as of June 2016 \cite{w3c2016webrtc}). He
loves learning new things and finding out how to use new technologies.

During leisure time, the author enjoys playing board and card games, has a
growing collection, visits board game fairs as an exhibitor and novelty
presenter, and works on multiple board games as an editor. Thus he had the idea
for the master thesis since the beginning of his master studies and is looking
forward to finally being able to realize this project as it merges two of his
favorite subjects, has very interesting mathematic and cryptographic problems to
be solved and also contains research parts about finding the right
technologies, how to use them and solve the associated challenges.

\section{Stakeholders}

\begin{description}
  \item[Players] want to play the chosen games against each other in a
  non-complicated way without technical issues.
  \item[Developers] want to use a programming library to reduce the work and
  needed time to implement new board game implementation by not needing to
  reinvent the wheel and ideally only needing to write their board game related program code.
  \item[Publishers] want to be able to reduce the financial costs
  involved for publishing online board game apps. They want to use the online
  implementation as a marketing instrument or to earn money.
  \item[Authors] want a way to easily playtest new ideas without producing
  physical components and being able to change them as the board or card game
  processes.\footnote{Thanks to Andreas Finkernagel from Pegasus Spiele for
  pointing out the idea that this common need could also be solved by this
  project}
  \item[System Administrators] want to have a low ressource load on the web
  servers to reduce the numbers of servers needed.
\end{description}

\section{Boundaries}

Creating a good looking user interface and user experience design is not scope
of this project. The complete set of requirements are defined in
\see{chap:requirements}.
