\newacronym{API}{API}{application programming interface}

\newglossaryentry{deck}
{
  name=deck,
  description={is a complete set of cards and usually has an identical
  back (but there may be decks of two-sided cards). A game may contain
  multiple different decks with the same or different backs}
}

\newglossaryentry{die}
{
  name=die,
  plural=dice,
  description={is a common element in board games to generate randomness. A die
  usually has 6 sides but there are also dice with a different number of sides.
  Most dice carry numbers from 1 to the number of sides to generate a random
  number, but there are also dice with different numbers, with symbols, or with
  colors. Each side of a die has the same probability to be chosen (“to be
  up”)}
}

\newglossaryentry{discard pile}
{
  name=discard pile,
  description={is a pile of cards which players discarded. Normally belongs to
  a draw pile. Often if a draw pile is empty, its discard pile is shuffled to
  form a new draw pile}
}

\newglossaryentry{draw pile}
{
  name=draw pile,
  description={is a pile of cards from which player may draw cards. Normally
  face-down if both sides do not show the same. Often accompanied by a
  discard pile. Can contain 0, 1 or multiple cards}
}

\newglossaryentry{ECMAScript}
{
  name=ECMAScript,
  description={ECMAScript is a programming language standard whose
  implementation for web browsers is called JavaScript}
}


\newglossaryentry{ECMAScript 2015}
{
  name={ECMAScript 2015},
  description={(formerly ECMAScript 6) is the sixth edition of the
  \gls{ECMAScript} standard. Thus, ECMAScript 2015 was the standard's latest
  release for JavaScript from mid-2015 until mid-2016}
}


\newglossaryentry{ESDoc}
{
  name={ESDoc},
  description={is a JavaScript documentation generator for \gls{ECMAScript
  2015}, using annotations similar to JavaDoc. It can be used to document
  modules, classes, methods, properties, and parameters including their types,
  private modifiers, descriptions, and tests through documentation block comments inside
  the code. The types and private modifiers of documentation blocks can be used
  by \glspl{IDE} for type checking and other code validation features}
}

\newglossaryentry{face}
{
  name=face,
  description={is the front-side of a card. A card is face-down when users
  are only able to see the backside. It must technically be impossible to know
  the front of a face-down card if the player did not already have the chance
  to see it}
}

\newglossaryentry{hand}
{
  name=hand,
  description={is the subset of cards hold by a player. The player usually sees
  the front of their cards and the other players only see the backsides. It must
  technically be impossible for other players to know the fronts if they did
  not already have the chance to see them. There are games in which cards are
  hold “backwards” so the player only sees the backside and other players see
  the front of their cards}
}

\newglossaryentry{hidden information}
{
  name={hidden information},
  description={is data that must technically not be known to other clients to
  avoid the possibility of cheating in board and card games}
}

\newglossaryentry{HTML5}
{
  name=HTML5,
  description={describes the current version of the HTML standard together with
  other specifications that collectively build the foundation of modern
  websites}
}

\newacronym[see={[Glossary:]{peer-to-peer}}]{P2P}{P2P}{peer-to-peer\glsadd{peer-to-peer}}

\newacronym{IDE}{IDE}{integrated development environment}

\newglossaryentry{peer-to-peer}
{
  name=peer-to-peer,
  description={is a distributed application architecture in which two or more
  clients connect to each other to directly exchange data instead of a server
  handling the data exchange}
}

\newglossaryentry{polyfill}
{
  name=polyfill,
  description={is \gls{ECMAScript} code implementing a standardized feature for
  webbrowsers currently not implementing the feature}
}

\newacronym[see={[Glossary:]{World Wide Web Consortium}}]{W3C}{W3C}{World Wide
Web Consortium\glsadd{World Wide Web Consortium}}

\newglossaryentry{WebRTC}
{
  name=WebRTC,
  description={(Web Real-Time Communication) is a set of JavaScript \glspl{API}
  to enable direct connections and data exchange between web browsers}
}

\newglossaryentry{World Wide Web Consortium}
{
  name={World Wide Web Consortium},
  description={is the main body for developing World Wide Web standards}
}
